\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking} % Options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}    % Options: 'blue', 'orange', 'green', 'red', 'purple', 'grey'

% Character encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Adjust the page margins
\usepackage[scale=0.85, top=2cm]{geometry}

% Personal data
\name{Oryan}{Mordoch} 
\title{Software Engineer}
\address{Israel}{Tel Aviv} 
\phone[mobile]{(+972) 52-585-6562}
\email{oryan.mordo@gmail.com}
\social[linkedin]{oryan-mordoch}
% \social[github]{yourgithub} % Add if you have one

% --- PREAMBLE BLOCK FOR COMPILATION STABILITY ---
\usepackage[english]{babel}
\usepackage{enumitem}
\setlist[itemize]{label=\textbullet, nosep, leftmargin=*}
% ------------------------------------------------

\begin{document}

%--- Make the header ---
\makecvtitle

%--- Summary ---
\vspace*{-2.9em}
\begin{center}
    \begin{minipage}{0.9\textwidth}
        \small\centering
        Ex-Microsoft Software Engineer and Ben Gurion University graduate currently driving critical infrastructure at Unit Ofek324. Specialized in designing large-scale distributed systems, Java-based microservices, and modern DevOps practices. Proven track record in architectural modernization, disaster recovery planning, and mentoring engineering teams.
    \end{minipage}
\end{center}
% \vspace*{0.1em}

%--- Experience ---
\section{Professional Experience}

\cventry{Jan 2024 -- Present}{Backend Software Engineer}{Ofek324 (IAF - Data Team)}{Tel Aviv}{}{
    \begin{itemize}
        \item \textbf{Architecture \& High Availability:} Designed and implemented an Active-Active Disaster Recovery (DR) architecture for critical CI/CD infrastructure, ensuring zero-downtime availability for mission-critical systems.
        \item \textbf{Legacy Modernization:} Led the end-to-end modernization of legacy systems, upgrading services from Java 8/11 to Java 21 within a Spring Boot environment, significantly improving performance and maintainability.
        \item \textbf{DevOps Orchestration:} Built and maintained robust CI/CD pipelines utilizing Jenkins, Docker, Kubernetes (K8s), Helm, and OpenShift, streamlining deployment processes across environments.
        \item \textbf{Monitoring \& Observability:} Designed a comprehensive monitoring ecosystem using Prometheus and Grafana for health tracking, and implemented custom Spring Boot alerts integrated with Splunk.
        \item \textbf{Mentorship:} Mentored junior developers, establishing code review protocols, enforcing best practices, and fostering a culture of professional growth.
        \item \textit{Clearance:} Hold Security Clearance Level 2, authorized for sensitive military systems.
    \end{itemize}
}

\vspace*{0.5em}

\cventry{Jan 2022 -- Dec 2023}{Backend Software Engineer Intern}{Microsoft R\&D}{Tel Aviv}{}{
\textit{Transitioned to full-time capacity for the final 14 months (Nov 2022 -- Dec 2023).}
    \begin{itemize}
        \item \textbf{Enterprise Development:} Developed and maintained features for one of the world's largest global compliance products, utilizing Java and Spring Boot to handle high-scale data loads.
        \item \textbf{Internal Tooling:} Python-engineered automation tools to analyze user needs and usage patterns, enabling data-driven decisions for internal resource management and capacity planning.
        \item Collaborated in an Agile environment to deliver production-grade code that adheres to strict quality standards.
    \end{itemize}
}

\vspace*{0.5em}

\cventry{Aug 2021 -- Jan 2022}{R\&D Support Student (Data Analyst)}{Morphisec}{Be'er Sheva}{}{
    \begin{itemize}
        \item \textbf{Data Analysis:} Conducted research and data analysis on security products using Python and Power BI to identify trends and anomalies.
        \item \textbf{Database Design:} Planned and designed a new database schema that was successfully implemented into the core company product to optimize data storage.
    \end{itemize}
}

%--- Education ---
\section{Education}
\cventry{Oct 2019 -- Sept 2023}{B.Sc. in Computer Science}{Ben Gurion University of the Negev}{Beer Sheva}{}{}

%--- Skills ---
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Java, Python3, Groovy, Shell/Bash, TypeScript, SQL.
    \item \textbf{Frameworks \& Libraries:} Spring Boot, Gradle, React.
    \item \textbf{DevOps \& Cloud:} Kubernetes, OpenShift, Docker, Jenkins, Helm, Nexus, Artifactory.
    \item \textbf{Databases \& Storage:} AWS S3, OracleDB, MongoDB, MySQL.
    \item \textbf{Monitoring:} Prometheus, Grafana, Splunk.
\end{itemize}

% --- LANGUAGES ---
\section{Languages}
\begin{itemize}
    \item \textbf{Hebrew:} Native
    \item \textbf{English:} Fluent 
\end{itemize}

\end{document}